### 2023-02-13 doc/manuscript/translocation.qmd
Remove specific examples from intro paragraph 2

Host evolution following disease-induced declines is one mechanism by which hosts can recover [@carlson2014; @searle2020]. Evolutionary rescue describes natural host evolution whereby rapid evolutionary changes originating from variation within a host population reverse ongoing population declines [@carlson2014]. In host-pathogen systems, evolutionary rescue is more likely to occur when hosts experience repeated selection events (e.g., through re-infections), there is a persistent pathogen reservoir or frequency-dependent infection dynamics, and populations experience increased per capita birth rates at small population sizes [@golas2021]. Evolutionary changes following disease-induced declines have been observed in black-lipped abalone populations suffering from herpes virus [@holland2022], little brown bat populations suffering from white-nose syndrome [@gignoux-wolfsohn2021], Tasmanian devils suffering from facial tumor disease [@epstein2016], and amphibian populations suffering from chytridiomycosis [@savage2016]. However, linking these selective responses directly to population recoveries, as necessary for evolutionary rescue, remains rare. Important for conservation action, selection that promotes recoveries of focal populations can also provide sources of resistant individuals to reestablish populations extirpated following disease emergence [@joseph2018; @mendelson2019]. These so-called "recovery engines" [@mendelson2019] -- where rescued (i.e., resistant and recovered) host populations are used to successfully repatriate other extirpated populations on the landscape -- are an intriguing management idea, but have not been successfully implemented in wildlife conservation efforts.

>>>>

Host evolution following disease-induced declines is one mechanism by which hosts can recover [@carlson2014; @searle2020]. Evolutionary rescue describes natural host evolution whereby rapid evolutionary changes originating from variation within a host population reverse ongoing population declines [@carlson2014]. In host-pathogen systems, evolutionary rescue is more likely to occur when hosts experience repeated selection events (e.g., through re-infections), there is a persistent pathogen reservoir or frequency-dependent infection dynamics, and populations experience increased per capita birth rates at small population sizes [@golas2021]. Evolutionary changes following disease-induced declines have been repeatedly observed in wildlife populations [@savage2016; @epstein2016; @gignoux-wolfsohn2021; @holland2022], but linking these selective responses directly to population recoveries, as necessary for evolutionary rescue, remains rare. Important for conservation action, selection that promotes recoveries of focal populations can also provide sources of resistant individuals to reestablish populations extirpated following disease emergence [@joseph2018; @mendelson2019]. These so-called "recovery engines" [@mendelson2019] -- where rescued (i.e., resistant and recovered) host populations are used to successfully repatriate extirpated populations on the landscape -- are an intriguing management idea, but have not been successfully implemented in wildlife conservation efforts.

<!--# Example text with more specific examples: black-lipped abalone populations suffering from herpes virus [@holland2022], little brown bat populations suffering from white-nose syndrome [@gignoux-wolfsohn2021], Tasmanian devils suffering from facial tumor disease [@epstein2016], and amphibian populations suffering from chytridiomycosis [@savage2016]-->
